HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-31 scnn.tex
small edits

\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere. Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
It is, however, restricted to those grid sampling sets. Similarly to the cubed-sphere, HEALPix is a composition of twelve grids. While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
\todo{How do thy handle boundaries?}
\TK{+1,good question}
% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere. Nope, the graph can adapt to any sampling.
% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e. (i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution. Do you think we should mention that? I think we should not.}
Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
Any convolution using directions on the sphere is not equivariant to translation and rotation.

@@

The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
Besides a different practical application, for which the method was designed, there are two important differences.
% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
% \TK{how is it different from us?}
Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
Finally, while the rotation invariance is desirable, the statistical layer used
% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
% \{TK} this should be explained earlier
may not capture the information in an optimal way
\todo{and hinders performance (should be empirically verified)}.
\TK{This is a strong claim, can we support this?}
Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
% While that may not be ideal, it was shown to work well in practice.
% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}

\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}
The use of the statistical layer is optional.
In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
\TK{why is this section in TODO?}

@@

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
\begin{equation} \label{eqn:graph_convolution_spatial}
	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
\end{equation}
In \ref{sec:heat_diffusion} we present an example application of graph-based convolution to a simple heat-diffusion problem.
% \textbf{Example.}
% Let us consider the heat diffusion problem
% \begin{equation} \label{eqn:heat_equation}
% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
% \end{equation}
% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
% \begin{equation*}
% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
% \end{equation*}
% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$. Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere. \figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$. By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}). While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution. For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.

@@

Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
\begin{equation} \label{eqn:graph_convolution_cheby}
	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
\end{equation}
where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$. While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$. Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood. That results in easier learning when optimizing the parameters $\theta$.
Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}. While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
In practice, we found out that Chebyshev polynomials are slightly more stable in our experiment \TK{slightly more stable than what?}.
We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$. On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}

@@

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network can be defined as
\begin{equation}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC
\end{equation}
\TK{what is the meaning of $\circ$ here?}
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

We observe that the PSD is unable to perform the desired task.
The main reason is that the two different models were designed to have very similar PSDs (see \figref{psd_sigma3}).
As a result, one needs to use other statistics to solve the problem.
In this case, the histogram features allow for a significant improvement over the PSD ones.
Unfortunately, while the histogram features contain information about the distribution of pixels, they do not include any spatial information.
In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
Note that without this graph structure, a fully connected neural network approach would have to be used.
Problematically, fully connected neural networks do not scale well with the number of pixels.
\TK{I don't understand this comment.}

We tried several different spherical neural network architectures and observed the following results.
First, Chebyshev polynomial seems more stable than monomials \TK{what are monomials? stable in what sense?}.
Nevertheless once the network is trained, we could not observe a significant accuracy difference.
Second, using a statistical layer improved the result unlimited for our problem.
We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse.
Third, the use of the dropout\TK{was dropout mentioned before?} layer did not help in the presence of noise.
This is probably due to the fact that the dataset was augmented indefinitely through the addition of noise.
Fourth, especially for the more difficult cases, orders 2 or 4 and large noise levels, a large architecture with many filters and many training iterations were necessary to achieve high accuracy levels.

>>>>

\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere. Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
It is, however, restricted to those grid sampling sets. Similarly to the cubed-sphere, HEALPix is a composition of twelve grids. While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
\todo{How do they handle boundaries?}
\TK{+1,good question}
\nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was: 
\emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."} 
Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable. As for the equirectangular grid, it is equivalent to a cylinder. So I guess they take the standard image processing border conditions (reflective).
I do not think we should mention any of that in the paper.
}
% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere. Nope, the graph can adapt to any sampling.
% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e. (i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution. Do you think we should mention that? I think we should not.}
Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
Any convolution using directions on the sphere is not equivariant to translation and rotation.

@@

The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
Besides a different practical application, for which the method was designed, there are two important differences.
% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
% \TK{how is it different from us?}
Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
Finally, while the rotation invariance is desirable, the statistical layer used
% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
% \{TK} this should be explained earlier
may not capture the information in an optimal way
\todo{and hinders performance (should be empirically verified)}.
\TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right? We should probably soften it a bit. However the main idea is correct. If you compute some statistics on some features, you lose some information and may get worse results. }
Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
% While that may not be ideal, it was shown to work well in practice.
% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}

\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
The use of the statistical layer is optional.
In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
\TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}

@@

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
\begin{equation} \label{eqn:graph_convolution_spatial}
	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
\end{equation}
In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
% \textbf{Example.}
% Let us consider the heat diffusion problem
% \begin{equation} \label{eqn:heat_equation}
% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
% \end{equation}
% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
% \begin{equation*}
% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
% \end{equation*}
% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$. Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere. \figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$. By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}). While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution. For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.

@@

Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
\begin{equation} \label{eqn:graph_convolution_cheby}
	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
\end{equation}
where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$. While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$. Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood. That results in easier learning when optimizing the parameters $\theta$.
Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}. While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e. optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$. On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}

@@

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network can be defined as
\begin{equation}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
\end{equation}
\TK{what is the meaning of $\circ$ here?}\nati{where $\circ$ is the composition operator between two layers.}
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

We observe that the PSD is unable to perform the desired task.
The main reason is that the two different models were designed to have very similar PSDs (see \figref{psd_sigma3}).
As a result, one needs to use other statistics to solve the problem.
In this case, the histogram features allow for a significant improvement over the PSD ones.
Unfortunately, while the histogram features contain information about the distribution of pixels, they do not include any spatial information.
In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
Note that without this graph structure, a fully connected neural network approach would have to be used.
Problematically, fully connected neural networks generally scales squarely with their number of inputs.
\TK{I don't understand this comment.} \nati{Maybe we should leave it out then. It is not that important.}

We tried several different spherical neural network architectures and observed the following results.
First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more steadily decrease.
%\TK{what are monomials? stable in what sense?}
Nevertheless once the network is trained, we could not observe a significant accuracy difference.
Second, using a statistical layer improved the result unlimited for our problem.
We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse.
Third, the use of the dropout\TK{was dropout mentioned before?} \nati{Probably not. But to keep it simple, we may just add a footnote or a reference.} layer did not help in the presence of noise.
This is probably due to the fact that the dataset was augmented indefinitely through the addition of noise.
Fourth, especially for the more difficult cases, orders 2 or 4 and large noise levels, a large architecture with many filters and many training iterations were necessary to achieve high accuracy levels.
